Title of the document here

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Results analysis

The data was collected with a questionnaire consisting of 15 questions.
Re

>>>>

The data was collected with a questionnaire consisting of 15 questions. The data has been analysed with simple descriptive analysis where mean values have been the main source to analyse the readability of a language (RQ1). Correlation between the independent and dependent variables have been the main analysis to answer SRQ1 and SRQ2. Score ranges have been used to analyse the strength of replies. More advanced data analysis methods have not been utilized due to the relatively low number of respondants.
